\documentclass[11pt,a4paper]{moderncv}
\usepackage{cv}

\tlmaxdates{2009}{2016}

\firstname{Tereza}
\familyname{Papouskova}
\address{20 Fleischnerova street}{635 00 Brno, Czech Republic}
\mobile{+420 776 571 348}
\email{tereza.papouskova@gmail.com}
\extrainfo{\linkedin~\httplink{www.linkedin.com/in/tdolezalova}}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle

\section{Professional Experience}

\tlcventry[timelinecolor]{2014}{2015}{Lawyer}{Office of the Public Defender of Rights}{Brno}{Czech Republic}{Working in the Department of Protection of Persons Restricted in their Freedom meant being a~member of a team carrying out tasks of the OPCAT national preventive mechanism: monitoring all places of de iure and de facto detention. Besides that I also processed individual complaints related mainly to public guardianship, social care facilities and psychiatric hospitals.\vspace{.01cm}\contact{Údolní 39, 602 00 Brno, Czech Republic}{+420542542484}{}{www.ochrance.cz}}

\medskip

\tlcventry[timelinecolor]{2013}{2014}{Intern}{Constitutional Court of the Czech Republic}{Brno}{Czech Republic}{My internship in this eminent institution consisted of the screening of complaints and assessing their admissibility, researching various topics and drafting concrete decisions. I was supervised by David Kosař, who is an assistant of the judge Kateřina Šimáčková.\vspace{.01cm}\contact{Joštova 8, 660 83 Brno, Czech Republic}{}{4775@mail.muni.cz}{www.usoud.cz}}

\medskip

\tlcventry[timelinecolor]{2011}{2014}{Research Fellow}{Czech Center for Human Rights and Democratization}{Brno}{\mbox{Czech Republic}}{Internship in an impartial academic body focusing on research in the human rights field included publishing articles on business and human rights in a monthly issued bulletin, organizing conferences and debates and helping with fundraising. I was also a web master and maintained database of subscribers to the bulletin.\vspace{.01cm}\contact{Turgeněvova 16, 618 00 Brno, Czech Republic}{}{hsmekal@fss.muni.cz}{www.centrumlidskaprava.cz}}

\medskip

\tldatelabelcventry[timelinecolor]{2013}{spring 2013}{Human Rights Council Intern}{Office of the United Nations High Commissioner for~Human Rights}{Geneva}{Switzerland}
{Assisting Human Rights Council Complaint Procedure Unit included handling confidential communications on human rights violations from all over the world and drafting of monthly reports. I also contributed to preparation and servicing of the 22nd session of the Human Rights Council and the 12th session of the Working Group on Communications.\vspace{.01cm}\contact{52 rue des Pâquis, CH-1201 Geneva, Switzerland}{}{llupoli@ohchr.org}{www.ohchr.org}}

\medskip

\tlcventry[timelinecolor]{2011}{2012}{Talent Acquisition Intern \& Corporate Giving Program Coordinator}{Red~Hat~Czech, Ltd.}{Brno}{Czech Republic}{My main tasks included supporting recruiters, more than 220 associates joined the company being advised and helped by me. Based on my strong commitment I have also taken over the role of the coordinator of Brno office's corporate giving program and greatly contributed to the successful launch of Red Hat's charitable program in the Czech Republic.\vspace{.01cm}\contact{Purkyňova 99, 612 00 Brno, Czech Republic}{+420 532 294 111}{}{www.cz.redhat.com}}

\section{Education}
\tlcventry[timelinecolor]{2012}{2014}{Master}{Masaryk University, Faculty of Social Studies}{Brno}{Czech Republic}{Final Thesis \emph{Institutional Replacement: the Case of Replacing The United Nations Commission on Human Rights by the Human Rights Council}}
\tlcventry[timelinecolor]{2010}{2015}{Master}{Masaryk University, Faculty of Law}{Brno}{Czech Republic}{Final Thesis \emph{Transferability of an Individual's Fundamental Rights to a Group of Individuals in Theory and Practice}}
\tlcventry[timelinecolor]{2009}{2012}{Bachelor}{Masaryk University, Faculty of Social Studies}{Brno}{Czech Republic}{Final Thesis \emph{The Concept of Responsibility to Protect from the Perspective of the United Nations' Response to the Conflict in Southern Kyrgyzstan in June 2010}}

{\small
\subsection{Related Activities}
\cvline{Publications}{Cui liberi – Child Custody in the Case Law of the Constitutional Court and European Court of Human Rights [published in Czech]. \textit{Jurisprudence}, vol. 23, issue 4, 2014. ISSN 1802-3843.}
\cvline{Academia}{Research assistant at the Department of Constitutional Law and Political Science}
\cvline{Competitions}{4th place at Telders Moot Court Competition in 2014, Overall winner of Czech Human Rights Moot Court in 2012}
\cvline{Summer courses}{Alternative Dispute Resolution -- Mediation (Central European University, Hungary), European System of Human Rights Protection (Viadrina University, Germany), Visegrad Summer School (Villa Decius Association, Poland), Borders of Europe (University of Ljubljana, Slovenia), How to Do a Social Research? (Masaryk University)}
\cvline{Coursera}{Computing for Data Analysis, Model Thinking, Statistics One}
\cvline{Other activities}{Participation in EU Model at Prague Student Summit, membership in Student Section of International Institute of Political Studies and Masaryk University Debate Club}
}

\section{Languages}
\cvlanguage{Czech}{Native speaker}{}
\cvlanguage{English}{Advanced}{Certificate in Advanced English (level C1)}
\cvlanguage{French}{Upper-Int.}{Diplom Élementaire de Langue Française (level B2)}
\cvlanguage{Russian}{Pre-Intermediate}{}
\cvlanguage{German}{Beginner}{}

\section{Volunteering}
\tldatelabelcventry[timelinecolor]{2014}{spring 2014}{The League of Human Rights}{}{Brno}{Czech Republic}{Assisting with research and drafting of documents concerning Juvenile Justice project.}
\tlcventry[timelinecolor]{2012}{2013}{Nesehnuti: Independent Social Economic Movement}{}{Brno}{Czech Republic}{Helping with campaign calling for inclusion of migrants into public health insurance system.}
\tlcventry[timelinecolor]{2011}{2013}{Forum 2000}{}{Prague}{Czech Republic}{Accompanying and assisting delegates during the annual conference Forum 2000.}
\tldatelabelcventry[timelinecolor]{2012}{spring 2012}{Intersob}{}{Brno}{Czech Republic}{Main organizer of a competition for high school students organized by MU.}
\tlcventry[timelinecolor]{2011}{2012}{Department of Pediatric Oncology}{}{Brno}{Czech Republic}{Being with hospitalized children, helping them to overcome the difficult period in their lives.}
\tlcventry[timelinecolor]{2010}{2011}{K-SCUK}{}{Brno}{Czech Republic}{Co-organizer of a training for solvers of MU correspondence seminars.}
\tldatelabelcventry[timelinecolor]{2010}{summer 2010}{Museum of Folk Architecture}{}{Pereyaslav-Khmelnytskyy}{Ukraine}{Helping with maintenance of the museum (cooperation mediated by INEX-SDA).}

\section{Interests}
\cvline{Dancing}{Contemporary -- main roles in performances MáMě and PŮLměSIC.}
\medskip

\cvline{Piano}{School-leaving exams at school of arts.}
\cvline{Sports}{Climbing, swimming, squash, frisbee.}
\cvline{Games}{Board games, role playing games etc.}

\end{document}

%% end of file `template_en.tex'.
